---
title: "Snakes and Ladders"
author: "Matt"
date: "2/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document contains student solutions to the snakes and ladders problem. Students will add to this file using the outline below. Write your name (using three hashtags), then below create an R code block and insert your code. Save the .rmd file, then knit the document to update the html output. Then submit a pull request to merge your changes to the main repository.

### Jeff Kravitz

```{r}
move <- 0
count <- replicate(1000, 0)
game_grid <- data.frame(c(3,6,9,10,14,19,22,24),c(11,17,18,12,4,8,20,16))
for (i in 1:1000) {
  spot <- 1
  while (spot <= 25) {
  move <- sample(1:6, 1)
  spot <- spot + move
  for (i in 1:8) {
    if (spot == game_grid[i,1]) {
      spot <- game_grid[i,2]
    }
  }
  count[i] = count[i] + 1
  }
}
avg_moves <- mean(count)
print(avg_moves)
```
###Angelina Vasquez Code
```{r}
save_rolls <- c()
for(sims in 1:1000){
  total_sum<-0
  number_of_rolls<-0
  while(total_sum < 25){
    number_of_rolls <- number_of_rolls+1
    total_sum <-total_sum+sample(c(1,2,3,4,5,6),1)
  }
  save_rolls[sims] <- number_of_rolls
}
mean(save_rolls)

#Just used the code you had in the example. Couldn't come up with a solution
```

